Final Model Analysis

### 2017-08-28 model fitting/final_model.Rmd
moved datadist to correct place

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
x <- read.csv("final_data.csv", head = TRUE)
library(survival); library(dplyr); library(rms)
```

@@

```{r, echo = FALSE}
# building model on train1 (df set to 5 for all splines at first, but setting tag and newline to 4 minimized AIC and performed best)
trainmodel <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = train1, x = TRUE, y = TRUE)
AIC(trainmodel, k = 2) # 54421.53
trainmodel
```

@@

```{r, echo = FALSE}
dd = datadist(x)
options(datadist = "dd")

x$text_length2 <- x$text_length**2 # for future use
x$sqrt_tag_score <- sqrt(x$avg_tag_score)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
x <- read.csv("final_data.csv", head = TRUE)
x <- as.data.frame(x)
library(survival); library(dplyr); library(rms)
```

@@

```{r, echo = FALSE}
# building model on train1 (df set to 5 for all splines at first, but setting tag and newline to 4 minimized AIC and performed best)
dd = datadist(x)
options(datadist = "dd")

trainmodel <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + pol(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = train1, x = TRUE, y = TRUE)
AIC(trainmodel, k = 2) # 54421.53
trainmodel
```

@@

```{r, echo = FALSE}
x$text_length2 <- x$text_length**2 # for future use
x$sqrt_tag_score <- sqrt(x$avg_tag_score)
